\cleardoublepage
\setsinglecolumn
\chapter*{\centering \Large Authorship Declaration}
\thispagestyle{empty}


In accordance with the regulations of the Graduate Research School, this thesis contains published work and/or work prepared for publications that are co-authored. The bibliographical details of the work and where it appears in the thesis are outlined below.

\begin{enumerate}
	\item \textbf{K. L. Lim} and T. Bräunl, "A Methodological Review of Visual Road Recognition Procedures for Autonomous Driving Applications," \textit{arXiv:1905.01635 [cs.CV]}, May. 2019.
	
	Paper presented as \textbf{Chapter~\ref{ch:vrreview}}. \\
	Estimated percentage of candidate's contribution is \textbf{90\%}.
	
	\item \textbf{K. L. Lim} and T. Bräunl, "A Review of Recent Visual Odometry Methods and Its Applications for Autonomous Driving," %\textit{arXiv:1612.06830 [cs]}, Dec. 2016.
	
	Paper presented as \textbf{Chapter~\ref{ch:voreview}}. \\
	Estimated percentage of candidate's contribution is \textbf{90\%}.
	
	\item R. G. Reid, \textbf{K. L. Lim} and T. Bräunl, "Cooperative Multi-Robot Navigation --- SLAM, Visual Odometry and Semantic Segmentation," in \textit{Cooperative Localization and Navigation: Theory, Research, and Practice}, C. Gao, Ed. Boca Raton: CRC Press, 2019, [in press].
	%pp. 15--64
	
	Paper presented as \textbf{Chapter~\ref{ch:cmrn}}. \\
	Estimated percentage of candidate's contribution is \textbf{30\%}.
	
	\item \textbf{K. L. Lim}, T. Drage and T. Bräunl, "Implementation of semantic segmentation for road and lane detection on an autonomous ground vehicle with LIDAR," in \textit{2017 IEEE International Conference on Multisensor Fusion and Integration for Intelligent Systems (MFI)}, Daegu, 2017, pp. 429--434. doi: 10.1109/MFI.2017.8170358
	
	Paper presented as \textbf{Chapter~\ref{ch:semseg}}. \\
	Estimated percentage of candidate's contribution is \textbf{70\%}.
	
	\item \textbf{K. L. Lim}, T. Drage, R. Podolski, G. Meyer-Lee, S. Evans-Thompson, J. Y.-T. Lin, G. Channon, M. Poole, and T. Bräunl, "A Modular Software Framework for Autonomous Vehicles," in \textit{2018 IEEE Intelligent Vehicles Symposium (IV)}, Changshu, 2018, pp. 1780--1785. doi: 10.1109/IVS.2018.8500474
	
	Paper presented as \textbf{Chapter~\ref{ch:modular}}. \\
	Estimated percentage of candidate's contribution is \textbf{35\%}.
	
	\item \textbf{K. L. Lim}, T. Drage, C. Zhang, C. Brogle, W. W. L. Lai, T. Kelliher, M. Adina-Zada and T. Bräunl, "Evolution of a Reliable and Extensible High-Level Control System for an Autonomous Car," \textit{IEEE Transactions on Intelligent Vehicles}. doi: 10.1109/TIV.2019.2919459 [in press].
	%vol. 1, no. 1, pp. 33–-55, 2016.
	
	Paper presented as \textbf{Chapter~\ref{ch:evo}}. \\
	Estimated percentage of candidate's contribution is \textbf{25\%}.
	
	\item C. Brogle, C. Zhang, \textbf{K. L. Lim} and T. Bräunl, "Hardware-in-the-Loop Autonomous Driving Simulation without Real-Time Constraints," \textit{IEEE Transactions on Intelligent Vehicles}. doi: 10.1109/TIV.2019.2919457 [in press].
	%vol. 1, no. 1, pp. 33–-55, 2016.
	
	Paper presented as \textbf{Chapter~\ref{ch:sim}}. \\
	Estimated percentage of candidate's contribution is \textbf{20\%}.
	
	\item \textbf{K. L. Lim}, S. Speidel and T. Bräunl, "REView: A Unified Telemetry Platform for Electric Vehicles and Charging Infrastructures," in \textit{Connected Vehicles in the Internet of Things: Concepts, Technologies and Frameworks for the IoV}, Z. Mahmood, Ed. New York: Springer, 2019, [under review].
	%pp. 15--64
	
	Paper presented as \textbf{Chapter~\ref{ch:review}}. \\
	Estimated percentage of candidate's contribution is \textbf{65\%}.
	
	\item \textbf{K. L. Lim}, S. Speidel and T. Bräunl, "A Comparative Study of AC and DC Electric Vehicle Charging Station Usage," \textit{Renewable \& Sustainable Energy Reviews}, [under review].
	
	Paper presented as \textbf{Chapter~\ref{ch:charging}}. \\
	Estimated percentage of candidate's contribution is \textbf{60\%}.
\end{enumerate}

\pagebreak

\noindent The candidate's statement regarding his contribution to each of the works listed above are correct.
\vspace{8ex}

\begin{table}[ht]
	\centering
	\renewcommand{\arraystretch}{.1} % Default value: 1
	\floatsep -10cm
	\begin{tabular}{p{0.2\columnwidth}p{0.6\columnwidth}p{0.2\columnwidth}}
		Kai Li Lim & \centering  & \multicolumn{1}{r}{} \\ \midrule
		PhD Candidate     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\[8ex]
		Thomas Drage & \centering  & \multicolumn{1}{r}{} \\ \midrule
		Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\[8ex]
		Stuart Speidel & \centering  & \multicolumn{1}{r}{} \\ \midrule
		Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\[8ex]
		Robert G. Reid & \centering  & \multicolumn{1}{r}{} \\ \midrule
		Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\[8ex]  
		Chao Zhang &\centering  & \multicolumn{1}{r}{} \\ \midrule
		Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\[8ex]
		Craig Brogle &\centering  & \multicolumn{1}{r}{} \\ \midrule
		Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\%[8ex]
		%William W. L. Lai &\centering  & \multicolumn{1}{r}{} \\ \midrule
		%Co-author     & \multicolumn{1}{c}{Signature} & \multicolumn{1}{r}{Date} \\
	\end{tabular}
\end{table}

\begin{samepage}
	\noindent I, Thomas Bräunl, hereby certify that the students' statements regarding their contribution to each of the works listed above are correct. As all co-authors' signatures could not be obtained, I hereby authorise the inclusion of co-authored work in the thesis.
	
	\vspace{6ex}
	
	\begin{table}[h]
		\flushleft
		\begin{tabular}{r}
			Coordinating Supervisor signature: \\
			Date:\\
		\end{tabular}
	\end{table}
\end{samepage}