% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      
I am thoroughly humbled by all the support that I have received throughout my candidacy, and the mere words that are expressed here could not possibly contain my utter appreciation. Prof Thomas Br\"aunl, adviser nonpareil. His progressive approach, amiability and field acumen has imbued me with invaluable exposures and opportunities, along with the establishment of professional networks that are otherwise unattainable under conservative supervisions.

Prof Victor Sreeram, my co-supervisor who is always available with his sound encouragements. Dr Du Hyunh and Dr Wei Liu for the valuable guidance during my albeit short tenure at CSSE. Ms Linda Barbour, who has professionally proofread all our publications; Mr Ivan Neubronner, who has technically cooperated with the maintenance of the charging infrastructures; and the EECE administrative team for assisting with my numerous requests and paperwork. 

Dr Joanne Edmondston for her kind advises and support especially during my supervision changes, and the GRS as a whole for its excellent HDR support, and most importantly accepting the thesis as a series of publications, which have encouraged the verification of results through peer review and improved time (and sanity) management. 

Dr Sally Male and Prof Dilusha Silva for the opportunity to be part of the engineering design project teams. This unit has benefited me as much as it did with the students. Dr Jonathan Whale for his insights toward WA's electromobility problem. Prof Farid Boussaid for his consistent concerns and interest in my work.  

I have thoroughly enjoyed the companionship and the camaraderie of my fellow colleagues throughout my candidacy. Franco Hidalgo, Marcus Pham and Thomas Drage are some of the best people I can rely upon for peer support and beyond. I am grateful to my friends and co-authors throughout the years at The REV Project, especially Chao Zhang and Craig Brogle, and to Dr Robert Reid and Dr Stuart Speidel for the manuscript suggestions and collaborations. 

I would also like to thank the many anonymous reviewers and publication editors for their insightful comments that led to the presentation of quality manuscripts. Subsequently to thesis examiners, Prof Albert Y. Zomaya, Dr Charles Karl, Dr Jens Berger and Prof Lance C. C. Fung for their time and excellent feedback. %leading to this finalisation.

I humbly appreciate the support of our sponsors. Thanks to Synergy and Galaxy for sponsoring the maintenance of the charging infrastructures, and to Nvidia for providing the GPUs for my research.% including this Titan V that I will be using to compile this thesis. 

To my friends dotted around the world, thank you for your thoughts, well-wishes, conversations and instant messages, especially to Jia Rong Gow, Leslie Tiong, Arvind Krishnasamy and Quang Nguyen. 

To my extended Lim and Chuah families, thank you for all your support, companionship and encouragements throughout since my very early years. I extend this thanks to all my personal and family friends.

I am grateful to the Ooi and Chee families who have taken care of me like one of their own and allowing me to accumulate probably too many possessions in my room.

To my brother Kai Shen at the Harvard T.H. Chan School of Public Health, thank you for the discerning advises and help on data analytics, especially on graph generation, as well as putting up with my routine calls for guild raids.

I would like to express my deepest gratitude to my parents, Eng Yong Lim and Sook Yean Chuah for their constant encouragements and unwavering trust while enduring my incessant antics throughout the years.

This research was supported by an Australian Government Research Training Program (RTP) Scholarship, but it will never be just without due acknowledgements to the people who contributed towards its realisation. From my MSc supervisor Prof Kah Phooi Seng who prepared me with the initial research training, the Department of Education for offering this scholarship, to the HDR Scholarships Committee who miraculously believed in my abilities enough to endow me with this scholarship. More importantly to everyday Australian taxpayers who enabled the creation of this budget. Hopefully, this thesis serves as one of the better outcomes of diligent tax filings.


   %I would like to take this opportunity to reiterate that Prof Thomas Br\"aunl is the best research supervisor anyone could ever ask for, and I would not have it any other way (I did not had many supervisors to begin with).


\end{acknowledgements}

%nonpareil acumen

%serves as one of the better outcomes from diligent tax filings

%who maraculously thought it was a good idea to hand me a $200,000 scholarship package
%And I would like to acknowledge ...
%
%This research was supported by an Australian Government Research Training Program (RTP) Scholarship.
%
%This research was funded by [insert name of grant and grant identification numbers].
%
%Technical assistance was kindly provided by [insert name of assistant(s)] for [insert description of assistance] that is described in [insert location in thesis].

%GRS, Ivan, Linda
%REV, Marcus, Franco, Thomas, Craig, Chao
%coauthors
%reviewers
%brother, stata family, friends
%synergy, jwhale, reviewers